%!TEX root = ../report.tex

% 
% Overview
% 

\section{Overview} % (fold)
\label{sec:overview}


This Section will provide an overview over this topic providing background. The Section~\ref{sec:objectives} will address the objectives for this thesis work. Section~\ref{sec:related_work} will explore different yet related work to this program. Section~\ref{sec:architecture} will describe the architecture of the proposed solution. Section~\ref{sec:evaluation} will explain how this solution will be evaluated and I will conclude on Section~\ref{sec:conclusions}.

\subsection{Procedural Generation} % (fold)
\label{sub:procedural_generation}

\emph{Procedural Generation} is the algorithmic generation of content instead of the usual manual creation of content. This can be applied in almost all forms of content, but is mostly used in graphics creation and sound (music and synthetic speech).

The key property of procedural generation is that it describes the data entity, being it geometry, texture or effect, in terms of a sequence of generation instructions rather than as a static block of data \cite{Kelly}. This allows the production of big volumes of detailed, and high quality graphic content without the costs, both in time and price, of manual content creation.

In the following sections some techniques of procedural modeling will be detailed.

% subsection procedural_generation (end)
%\subsection{Overview - Procedural Modelling Techniques} % (fold)
%\label{sub:procedural_modelling_techniques}

\input{sections/overview/1-Fractals.tex}

\input{sections/overview/2-cellular_automaton.tex}

\input{sections/overview/3-L-Systems.tex}

\input{sections/overview/4-shape_grammars.tex}

\input{sections/overview/5-tiling.tex}

\input{sections/overview/6-noise.tex}

%\input{sections/overview/7-voxels.tex}

%\input{sections/overview/8-architectural_styles.tex}

%\input{sections/overview/9-urban_planinng.tex}

% subsection procedural_modelling_techniques (end)

\input{sections/overview/LOD.tex}

\subsection{Graphic Tools} % (fold)
\label{sub:graphic_tools}
There are several application programming interfaces for graphic content creation, but the most known ones are DirectX and OpenGL. 

DirectX is a collection of multimedia APIs created by Microsoft for their platforms. It includes the Direct3D API. This tool has evolved very much since it was released and supports the state of techniques such as hardware acceleration and so forth.  On the other hand this system is only supported by Microsoft platforms and since this work should not be limited to the Microsoft platforms, this tools will not be used. 

OpenGL is an open-source library that is widely used. This system will be better explained in the next section.

% subsection graphic_tools (end)

\input{sections/Overview/OpenGL.tex}
%\input{sections/Overview/DirectX.tex}
%\input{sections/Overview/Pict3D.tex}
%\input{sections/Overview/CAD-tools.tex}
%\input{sections/Overview/CEPL.tex}





% section overview (end)