%!TEX root = ../report.tex

% 
% Objectives
% 

\section{Objectives}
\label{sec:objectives}

The world population has grown at a faster and faster pace, and  which is causing overcrowding and lack of resources in various locations of the globe. For example in the Emirates, the economic boom supported by the oil business is creating lots of work oportunities, thus thousands of people from everywere in the world are moving there. However the country was not prepared to accommodate the growing population currently living there. 
%To solve this problem of overpopulation that occurs there, and in other countries like China, new big cities are being built in the desert completely from scratch. An example of these cities is the city of Maasdar in Abu Dhabi. This city designed by Foster and Partners and currently being built in the desert and an estimated cost between $US\$18 and 19 billion$. Who is responsible for a project of this size can not afford to make a mistake in choosing the location or city setting.
%To test these factors is necessary to create models , only in contrast to the relatively small cost of creating manually using traditional techniques , model a single building with some variations , nestad situations have to be modeled an entire city and even variations additional. This  design phase is therefore very costly in time and effort required to enable them to obtain the best possible result.

%The objectives of this project are to study the existing approaches to Procedural Generation and provide a solutions to the kind of problems, like the new city in Abu Dabi stated above, through the implementation of mechanisms for procedural generation of architectural form, with application to the generation of large amounts of geometry, such as of urban environments or complex models.

The overall goal of this work is to build a GD tool that solves the performance problems that raise with the modeling and generation of large amounts of geometry. It should be an easy to use tool with very high performance that will be focus on model visualization removing features regarding interactive model manipulation.

It should be able to support Immediate Feedback for much larger models than the current GD tools can handle. This system should also provide a significant amount of geometric primitives such as \emph{boxes}, \emph{cylinders} or \emph{spheres} that will allow users to model.

The goal is to build a programming interface, that is how users will interact with the system, and it should be easy and simple to use yet broad and powerful to give them freedom to create. This will be the visible part of the system. 

After there is the \textbf{GPU communication} module that implement the functions provided. This module will generate the geometry description, create the windows and transfer the data to the GPU. This module will implement a set of techniques that will 

The \textbf{GPU pipeline} is where the geometry will be generated and is explained in Section~\ref{sub:modern_opengl}.


This work is being developed in the context of the Rosetta that is also a GD tool that helps architects and designers to develop their work procedurally. Rosetta is an extensible IDE based on \textbf{DrRacket} and built in Racket. 

In this context the module will act as a fast preview mode that allows the users to rapidly see the changes they make on their model during their creative process.

On the next section will be presented related works that have similar objectives.


%The world population has grown at a faster and faster pace, which is causing overcrowding and lack of resources in various locations of the globe. For example in the Emirates, the economic boom supported by the oil business is creating lots of work oportunities, thus thousands of people from everywere in the world are moving there. However the country was not prepared to accommodate the growing population currently living there. 
%To solve this problem of overpopulation that occurs there, and in other countries like China, new big cities are being built in the desert completely from scratch. An example of these cities is the city of Maasdar in Abu Dhabi. This city designed by Foster and Partners and currently being built in the desert and an estimated cost between $US\$18 and 19 billion$. Who is responsible for a project of this size can not afford to make a mistake in choosing the location or city setting.
%To test these factors is necessary to create models , only in contrast to the relatively small cost of creating manually using traditional techniques , model a single building with some variations , nestad situations have to be modeled an entire city and even variations additional. This  design phase is therefore very costly in time and effort required to enable them to obtain the best possible result.

%The objectives of this project are to study the existing approaches to Procedural Generation and provide a solutions to the kind of problems, like the new city in Abu Dabi stated above, through the implementation of mechanisms for procedural generation of architectural form, with application to the generation of large amounts of forms, such as of urban environments, buildings and ornaments efficiently and according to a particular architectural style models.

%With the large amount of very different techniques, explained in Section~\ref{sub:procedural_modelling_techniques}, one important part of this work is to know where to apply each techinque to obtain better results.
